%Acknowledgments

\renewcommand{\baselinestretch}{2}
\small\normalsize
\hbox{\ }
 
\vspace{0in}

\begin{center}
\large{Acknowledgments} 
\end{center} 

My PhD journey in UMD is definitely one of the most memorable experience in my life. 
I would like to share my deep appreciation to all the people who helped me along the road. 
This thesis cannot be finished without contributions from them.

At first, I am deeply grateful to my advisor, Prof.You Zhou, 
for his generous support and insightful guidance throughout my PhD.
I’m always inspired by his passion and curiosity across a wide range of fields as a researcher and impressed by his broad knowledge and scientific acumen. 
As an advisor, he is always patient in answering my questions and provides timely feedback which can help me complete my work efficiently.
He also encourages me to be confident, taught me how to prepare my presentation slide by slide, provides all the help he can whenever we met troubles that we cannot solve in the lab. 
I feel truly fortunate to have worked under his supervision, where I learned a lot not only for technical skills and knowledge but, equally, integrity and a rigorous attitude toward research.
Thank you for being such a wonderful advisor.

I believe people are drawn together by shared values, and Prof. Zhou has attracted a group of truly great person. 
I am deeply grateful to all members of the Zhou Lab.
I first thank Richmond (Shiwei) Wang for welcoming me to the lab and letting me shadow his experiments; I learned a lot about pulsed laser deposition from him, and despite long, tiring days, he always kept a smile. 
I also thank Lifu Zhang, an excellent researcher and generous person: our discussions consistently gave me valuable insights. 
I feel lucky to have Beini Gao as both a colleague and a friend; 
I’ve continually benefited from her expertise, energy, positivity, empathy, and readiness to help others.
She taught me a lot about optics and practical tips for 2D materials.
I’m grateful to my same-year colleague Ruihao Ni.
As this lab could not have been built without his effort and expertise. 
Thanks to Rundong Ma for countless daily helps and discussions on experiments and lab management.
I also appreciate Konstantin Davydov and Hassan Alnatah, who joined in the last year of my Ph.D. but still provided substantial help: Konstantin for keeping the lab organized and for his thoughtful questions and comments, 
and Hassan for his help on the polariton measurement, from which I learned a great deal. 
And thank you all guys with the invaluable discussion and moments. 
I wish you guys all the best in the future.

I'd also like to give special thanks to my PhD dissertation committee members for guidance: Prof. Thomas E. Murphy, Prof. Ichiro Takeuchi, Prof. YuHuang Wang, and Prof. Carlos A. Rios Ocampo. 
I also want to acknowledge the financial support from Ann G. Wylie Dissertation Fellowship, NSF, DOE and DARPA.

I am also grateful to our collaborator Prof.Mohammad Hafezi and his group members: Daniel Gustavo Suárez Forero, Supratik Sarkar, Mahmoud Jalali Mehrabad.
In particular, I thank Deric Session for his patient guidance on nanofabrication processes. 
I would like to thank our long term collaborators in Brookhaven National Lab: Suji Park and Houk Jang, for consistently providing high quality exfoliated monolayer TMDs. 
Thanks to Wenqi Zhu at NIST for providing high quality DBR substrates, and thanks to Prof. Stephen Forest, Prof. David Snoke and his student Qiaochu Wan for providing us withe the transferable DBR sample.

Thanks all the staffs in UMD Fablab: 
Mark Lecates, Tom Loughran, Jonathan A. Hummel, John Abrahams, Nam Kim, Daniel Lewis.
And AIM Lab Jiancun Rao for help with SEM,
SAC Karen Gaskell for the assistance with AFM and PFM.

I would also like to thanks the UMD MSE community. 
I am grateful to Achille Prete for his diligent work maintaining our lab and office facilities. I also thank Ms. Adire Parker for her help with paperwork and administrative support.

I am especially thankful to my UMD friends. 
Special thanks to Sheron (Chuanyu) Lian,my friend and close roommate. I was often the first to taste her cooking, from fresh baked tarts and cakes to delicious dishes. 
I still remember swimming with her and Rundong at the gym and then talking in the saun are the most relaxing moments of my time here. 
I am deeply grateful for her friendship and support since I first came to the U.S. 
Thanks as well to my MSE friends: Boyang Liu, Hongyi Sun, Chih-Yu Lee, Yi-Siou Hwang, Runze Li, and Sheng-Wei Wang.
The gathering lightened my life in UMD.

Finally, I wish to express my deepest gratitude to my parents in China. 
I am fortunate to have pursued my path with your unwavering support and encouragement.
Thank you for giving me the freedom to explore, for trusting my choices even when they took me far from home, and for standing behind me whenever I felt discouraged.
You taught me to work hard, to be curious, to act with integrity, and to treat others with kindness.
You have been my strongest support and my backbone. 

Thank you, Momo, my beloved kitty. 
You’re always there waiting when I come home. 
Your purrs and presence are the best stress relief.

The best thing I have had in UMD was meeting Yuxi at the initial stage of my PhD. 
He shared all my happiest, exciting moments, and also knows my every setback and frustration along the way. 
His constant encouragement and patience gave me the courage to move forward.
Our conversations spanning science, life, nature always heal me and get me inspired.
Thank you for just being yourself and walking in my life, bringing me different colors and experiences that I have never had in my life. 

\vspace{1ex}


