%Chapter 7

\renewcommand{\thechapter}{7}

\chapter{Summary and Outlook}
\label{chap7}
\section{Summary}

In this thesis, we explored the tightly bound excitons in TMDs on its exciton nonlinear interaction, and manipulate its interaction strength through:(1) quantum confinement through moire electrostatic superlattice in Chap.~\ref{chap4} and (2) cavity engineering in Chap.~\ref{chap6}. 

In Chap.~\ref{chap4}, we leverge the moiré electrostatic superlattice of twisted hBN to imprint nanoscale, quasi-one-dimensional potential wells into adjacent 2D semiconductors. 
At the moiré domain boundaries, strong in-plane fields reshape the optical reflectance of monolayer MoSe$_2$ and reveal intralayer excitons confined to $\sim$10~nm-wide strips. 
The confined response is linearly polarized, consistent with a quasi-1D exciton channel rather than a 2D sheet. 
Owing to their larger polarizability, Rydberg excitons experience even tighter localization under the same fields. 
From the confined spectra, we extract an exciton COM confinement length around $\sim$4~nm, which localized the exciton wavefunction and thus enhance the exciton interaction strength.
This can lower the optical density required to observe nonlinear shifts, and improves overlap with guided photonic modes along the boundary. 

In Chap.~\ref{chap5}, we demonstrated electrical control of multiple exciton species in trilayer WSe$_2$ and showed that the polaron regime yields a strong, gate-dependent nonlinear optical response at low excitation densities. 
The observed $\sim$10~meV nonlinear blueshift under CW excitation corresponds to an interaction strength on the order of $\mathrm{meV}\!\cdot\!\mu\mathrm{m}^2$, attributable to exciton–carrier (polaron) interactions enabled by the distinctive band structure of the trilayer system.

Based on this, we developed an electrically tunable 1D microcavity in Chap.~\ref{chap6}. 
As exptected, we observed robust strong coupling at 5~K with a Rabi splitting of $\sim$30~meV in trilayers that persists across wide gate ranges. 
Under resonant drive, only hole-doped trilayers showed blueshifts of both polariton branches, confirming polaron-mediated interactions; at higher powers the Rabi splitting decreased due to oscillator-strength bleaching. 
Together, these results demonstrate a bright, electrically tunable polaron–polariton platform that combines large oscillator strength with pronounced nonlinearity, providing a practical route toward the quantum nonlinear regime.

\section{Outlook: Roadmap towards the Blockade Regime}
The long-term goal is to realize few-photon nonlinear optics on TMD-based solid state platform.
This relies on the system with strong interactions among their components.
One key milestone is the Photon blockade: it occurs when the interaction energy $U$ exceeds the total linewidth $\gamma$ (the sum of cavity loss $\kappa$ and matter dephasing $\gamma_{X}$), i.e., when $U/\gamma \geq 1$. 
Prior demonstrations in atom–cavity and quantum-dot–cavity systems set practical targets for $U$, for the cavity quality factor $Q$ (and thus $\kappa$), and for spectral stability~\cite{Birnbaum2005-ix,} 
These benchmarks define the figures of merit our TMD–cavity devices aim to meet.

Motivated by this target, we first consider quantum confinement as a lever to increase $U$ and reduce $\gamma$. 
In-plane exciton localization and tighter photonic confinement both reduce the effective mode volume, enhancing the light–matter coupling $g \propto V_\mathrm{eff}^{-1/2}$ and, in turn, polariton–polariton interactions. 
Confinement can also suppress the exciton radiative decay and reach a narrower $\gamma$. 
While our current demonstration is limited in strength and scale, there are still some aspects we can further work: (i) engineer 0D potentials (patterned gates, strain-defined dots, or local thickness steps) to further localize the exciton COM wavefunction; (ii) co-localize the exciton trap with a photonic antinode
Taken together, these efforts directly raise $U/\gamma$.

In parallel, cavity optimization addresses the photonic loss channel $\kappa$. 
High-$Q$, all-dielectric transferable DBRs (to reduce absorption and scatter) and low-roughness lateral patterning (to control the in-plane mode) offer immediate paths to lower $\kappa$. 
Once $Q$ is improved, a decisive milestone is the Hanbury Brown–Twiss measurement of the second-order correlation $g^{(2)}(0)$ under resonant pumping to demonstrate the photon/polariton antibunching. 
This would provides a direct readout of few-photon nonlinearities and mark the progress toward blockade.

We can also apply the same confinement method to polaritons in trilayer WSe$_2$. 
Since the lower-polariton effective mass is smaller than the bare exciton’s, comparable potentials can yield tighter polariton mode areas and stronger interactions per photon. 
From the experiment aspect, this can be achieved through including shallow electrostatic traps, thickness-defined mesas aligned to cavity antinodes, and photonic lattices or patterned top DBR to form 0D polariton confinement. 
The main challenges are maintaining a high $Q$ during patterning and uniform gating. This requires careful process integration and control.

Finally, to improve measurement fidelity and sensitivity to oscillator-strength changes, can we try emission as the probe?
Cavity-enhanced PL or resonance fluorescence (with engineered out-couplers for efficient collection) can boost signal-to-background.
Crucially, emission-based $g^{(2)}(0)$ at the spectral peak of a single confined polariton offers a clean test for antibunching and saturation effects at the few-photon level.



% Example canonical references (adjust to your .bib):
% \bibitem{Birnbaum2005Nature} K.~M.~Birnbaum \textit{et al.}, Nature \textbf{436}, 87–90 (2005).
% \bibitem{Faraon2008NatPhys} A.~Faraon \textit{et al.}, Nat. Phys. \textbf{4}, 859–863 (2008).
% \bibitem{Reinhard2012NatPhoton} A.~Reinhard \textit{et al.}, Nat. Photonics \textbf{6}, 93–96 (2012).


